The starting grid in Formula 1: 2025

### 2025-12-12 inst/grid.Rmd
more output

    H <- list()
    for(i in 1:24){
        vec <- as.numeric(a[,1])
        vec[is.na(vec)] <- 0
        jj <- setNames(vec, rownames(a))
        H[[i]] <- ordervec2supp(jj) |> pwa3(geometric(lambda,grid_order[[i]]))
    }
    out <- hyper3()
    for(i in 1:24){
        out <- out + H[[i]]
    }
    return(out)
}
```

```{r calcpoll, cache=TRUE}
jj <- f1grid(0.5)
```

```{r maxcalc, cache=TRUE}
mH <- maxp(jj)
```

```{r}
mH
```

>>>>

    H <- list()
    for(i in 1:24){
        suppressWarnings(vec <- as.numeric(a[,1]))
        vec[is.na(vec)] <- 0
        jj <- setNames(vec, rownames(a))
        H[[i]] <- ordervec2supp(jj) |> pwa3(geometric(lambda,grid_order[[i]]))
    }
    out <- hyper3()
    for(i in 1:24){
        out <- out + H[[i]]
    }
    return(out)
}
```

```{r calcpolltime, cache=TRUE}
supptime  <- system.time(jj <- f1grid(0.5))
```

```{r maxcalctime, cache=TRUE}
maxtime <- system.time(mH <- maxp(jj))
```

```{r showresultstime}
supptime
maxtime
mH
pie(mH)
```

```{r domore, cache=TRUE}
o <- function(lambda){maxp(f1grid(lambda), give=TRUE)$value}
timeo1 <- system.time(l1 <- o(1.01))
timeo2 <- system.time(l2 <- o(1.02))
```

```{r}
timeo1
timeo2
l1
l2
```

```{r domanyLikes, cache=TRUE}
lam <- seq(from=0.9, to=1, len=17)
L <- sapply(lam, o)
```

```{r plotF1lamf, echo=TRUE, fig.cap="Log-likelihood function for lambda, the pole position measure"}
plot(lam, L - max(L), pch=16, type="b")
```

Figure \@ref(fig:plotF1lamf) shows a log-likelihood function for
$\lambda$.  It is very irregular, indicating that the optimization
routine is having difficulty finding a global maximum for all values
of $\lambda$.
